Bayesian Insights into Olive Oil Pricing Dynamics in Canada

### 2024-12-04 paper/paper.qmd
Add files via upload

>>>>

## API for Model

The Price Prediction API provides a RESTful endpoint that estimates product prices based on historical data and various market factors. The API is implemented using the R Plumber framework and incorporates a Bayesian regression model built with the rstanarm package.
API Specification:
Endpoint: GET /predict_price
Version: 0.0.1
Input Parameters:

old_price: Numeric value representing the previous price of the product (default: 1.75)
brand: Categorical variable indicating the product brand (default: "Aurora")
vendor: Categorical variable specifying the retail vendor (options: "Metro" or "Walmart")
month: Integer value representing the month (range: 7-12)

Model Architecture:
The prediction model utilizes Bayesian regression with the following components:

Intercept term (α)
Price coefficient (β) for previous price
Brand-specific effects (categorical coefficients)
Vendor-specific effects (categorical coefficients)
Monthly seasonal effects (categorical coefficients)

The prediction is generated through the following process:

Input validation and type conversion
Extraction of posterior samples from the trained model
Computation of predicted values using the linear combination:
predicted_price = α + β_old_price * old_price + β_brand + β_vendor + β_month
Calculation of the mean prediction from posterior samples

Output:
The API returns a JSON object containing:

estimated_price: The predicted price value based on the input parameters

The model is designed to capture market dynamics, brand positioning, vendor-specific pricing strategies, and seasonal variations in the olive oil market.
